Masterclass Assignment: Real-time Global Illumination

### 2018-01-13 docs/paper.tex
working on documentation

\begin{figure}[htbp]
  \centering
 \subfloat[Specular Cone]{\includegraphics[width=0.45\linewidth]{images/specularCone}}
 \hfill
 \subfloat[Diffuse Indirect Cones]{\includegraphics[width=0.45\linewidth]{images/indirectCones}}
 \caption{A side by side comparison of different render effects is always a good idea to demonstrate a choice of parameters or design of your shader. These were appropriated from \cite{Villegas2016}.}
\end{figure}

@@

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/full_render_01}
 \includegraphics[width=1.0\linewidth]{images/full_render_02}
 \includegraphics[width=1.0\linewidth]{images/full_render_03}
 \caption{\label{fig:reference}Three screenshots showing the full scene with a voxel resolution of $512^3$.}
\end{figure}

@@

\begin{figure}[htbp]\centering
\begin{center}
 \begin{tabular}{|c|c|c|c|}
 \hline
 Voxel Resolution & $256^3$ & $512^3$ & $768^3$ \\
 \hline
 \hline
 Frames per second & 60 & 60 & 60 \\
 \hline
 Memory usage & 1063MiB & 2615MiB & 6628MiB \\
 \hline
 Voxelisation & 2ms & 2ms & 2ms \\
 \hline
 Light Injection & 65ms & 378.5ms & 12294.5ms\\
 \hline
 Shading & 4.5ms & 4.5ms & 4.5ms \\
 \hline
 \end{tabular}
 \caption{\label{figure:performance} Averaged performance results when running with a NVIDIA GTX 1080 8GB at 2560x1080.}
\end{center}
\end{figure}

\section{Future Improvements}

>>>>

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/BRDF}
 \caption{A series of diagrams showing how the combination of a specular cone and multiple diffuse cones can be used to approximate a material BRDF. \protect\cite{Villegas2016} The diffuse cones form a normal-oriented hemisphere to approximate the diffuse reflections, whilst the specular cone follows the reflection vector and it's aperture varies dependent on the material roughness.}
\end{figure}

@@

Figure~\ref{figure:fullrender} shows a series of screenshots of my final results with all of the lighting passes enabled. Whilst I am pleased with the outcome, there are also a number of visual artefacts that I discuss in Section~\ref{section:improvements}. Figure~\ref{figure:performance} shows some performance metrics for the individual lighting passes at different voxel resolutions. Note that memory usage is high, even at low resolutions, as I opted to use dense 3D textures as opposed to sparse 3D textures. The time taken to perform the light injection pass also scales quite poorly at high resolutions because of this. Despite this, moving around the scene maintains a smooth 60 frames per second (limited by the OpenGL context), providing the user does not move the light. The voxelization and shading passes seem to scale very well with increased resolution, taking on average 2 and 4.5 miliseconds respectively at all of the tested resolutions.

\begin{figure}[htbp]\centering
\begin{center}
 \begin{tabular}{|c|c|c|c|}
 \hline
 Voxel Resolution & $256^3$ & $512^3$ & $768^3$ \\
 \hline
 \hline
 Frames per second & 60 & 60 & 60 \\
 \hline
 Memory usage & 1063MiB & 2615MiB & 6628MiB \\
 \hline
 Voxelization & 2ms & 2ms & 2ms \\
 \hline
 Light Injection & 65ms & 378.5ms & 12294.5ms\\
 \hline
 Shading & 4.5ms & 4.5ms & 4.5ms \\
 \hline
 \end{tabular}
 \caption{\label{figure:performance} Averaged performance results when running with a NVIDIA GTX 1080 8GB at 2560x1080.}
\end{center}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/full_render_01}
 \includegraphics[width=1.0\linewidth]{images/full_render_02}
 \includegraphics[width=1.0\linewidth]{images/full_render_03}
 \caption{\label{figure:fullrender}Three screenshots showing the full scene with a voxel resolution of $512^3$.}
\end{figure}

@@

\section{Future Improvements} \label{section:improvements}
